---
title: "Binomial & Random Variables"
author: "Kaffa Sakho"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
library(dplyr)
```

## **Binomial Distribution**

The package **"binomial"** is a set of functions that allow the computation and visualization of probabilities and other statistical measures of a **binomial random variable**.

The content of this guide for the binomial package is as follows:

1. Creating a Binomial Random Variable Object

2. Measures on a Random Variable

3. Different Combinations of k Successes in n Trials

4. Computing the Probabilities explain what this means include the code 

5. Computing & Visualizing Distributions  


### 1. Creating a Binomial Random Variable Object: bin_variable

A binomial random variable is a discrete random variable that determines the number of times a specific event occurs in a given number of trials. Therefore, to construct a random variable we need to know the number of trials and the probability of success of the event we are interested in. To create it, we use the function bin_variable() as follows: 

```{r}
n <- 12 # the number of trials
p <- 0.4 # the probability of success per trial
X <- bin_variable(n,p) # calling our random variable X
```

X is an object of class "binvar".

##### Methods of bin.variable

We can extract information about a random variable object by using methods like print() or summary().

print() prints the content of our binomial object X. 

```{r}
print(X)
```

We use summary() to get a comprehensive summary of our binomial object X. Here, summary() takes as argument an object of class "binvar" and outputs an object of class "summary.binvar"

```{r}
summary1 <- summary(X)
summary1
```

print() can also print the summary of our binomial random variable when given an object of class "summary.binvar" as input.
```{r}
print(summary1)
```

### 1. Measures of a binomial random variable

All below mentionned binomial random variable functions of measures take two inputs:

**n** is the number of trials.

**p** is the probability of succcess per trial.

The mean of a binomial random variable is the expected number of successes in a given number of trials. We calculate the mean of our binomial object as follows:

```{r}
bin_mean(n,p)
```

We calculate the variance of our binomial object as follows:
```{r}
bin_variance(n,p)
```

The mode of a binomial random variable is the most likely number of success in a given number of independent trials rounded to the greatest integer less than or equal to it. We calculate the mode of our binomial object as follows:
```{r}
bin_mode(n,p)
```

The skewness of a probability distribution of a random variable measures the asymmetry of the probability distribution of a random variable about its mean. We calculate the skewness of the distribution of our binomial object as follows:
```{r}
bin_skewness(n,p)
```

The kurtosis of a probability distribution of a random variable measures the tailedness of the probability distribution of random variable. We calculate the kurtosis as follows:
```{r}
bin_kurtosis(n,p)
```

### 3. Different Combinations of k Successes in n Trials: bin_choose

**Description**

To calculate the different number of ways to obtain k successes in n trials we use bin_choose(). 

**Arguments** 

bin_choose(n,k) takes two arguments: 
**n** is the number of trials
**k** is the number of successes. k cannot be greater than the number of successes. If k>n bin_choose will raise an error.

**Value**

The output value is a non-negative integer. 

**Example**

```{r}
k <- 4
bin_choose(n,k)
```
This means there are **495** ways of obtaining 37 successes in 43 trials. 

### 4. Computing the Probability of Successes: bin_probability

*Description*
After finding the different number of combinations, we can find the probability of obtaining k successes in n trials by using bin_probability().

*Arguments*

bin_probability(k,n,p) takes three arguments: 
**k** is the number of successes. k cannot be greater than the number of successes. If k>n bin_choose will raise an error.
**n** is the number of trials.
**p** is the probability of a success in one trial.

*Value*

The output value is a number between 0 and 1 both included.

*Example*

```{r}
bin_probability(k,n,p)
```

### 5. Computing & Visualizing Distributions 

**Distribution**

*Description*

The distribution of a random variable shows the different probability values across different possible number of successes under a given number of trials. 

*Arguments* 

bin_distribution takes in two arguments: 
**n** the number of trials.\
**p** the probability of success per trial.

*Example*

```{r}
distribution.table <- bin_distribution(n,p)
distribution.table
```
The output is a data frame with two columns. The first column shows the number of possible successes in n trials, and the second column shows the probability of obtaining that number of successes in n trials. This data frame has primary class "bindis".

We can graph the probability distribution using plot(). Here plot takes an object of class "bindis".

```{r}
plot(distribution.table)
```


**Cumulative Distribution** 

*Description*

The cumulative distribution of random variable at k successes is the probability that the number of successes is less or equal than k. We use bin_cumulative to obtain the cumulative probabilities.

*Arguments*

bin_cumulative takes in two arguments: 
**n** the number of trials\
**p** the probability of success per trial.

*Example*

```{r}
cumulative.table <- bin_cumulative(n,p)
cumulative.table
```
The output is a data frame that shows in the 2nd column the probabilities of obtaining k successes in n trials and in the 3rd column the probabilities of obtaining less or equal to k successes in n trials for any $0<k<n$. This data frame has primary class "bincum".

Moreover, we can visualize the cumulative probability distribution of a random variable using plot. Here, plot takes an argument of class "bincum".

```{r}
plot(cumulative.table)
```







