---
title: "Getting Started with Binomial"
author: "Kaffa Sakho"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

## **Binomial Distribution**

The package **"binomial"** is a set of functions that allow the computation and visualization of probabilities and other statistical measures of a **binomial random variable**.

The content of this guide for the binomial package is as follows:
1. Creating a Binomial Random Variable Object
2. Calculations on a random variable(mean,variance,mode,skewness,kurtosis)
3. Different Combinations of k Successes in n Trials
4. Computing the Probabilities explain what this means include the code 
5.  Computing the distributi ons (both normal and cumulative) explain what they mean include the code
6. Visualizing Distributions of a Binomial Random Variable
- explain plot.bindis
- include graph
- explain plot.bincum
- include graph

### 1. Creating a Binomial Random Variable Object: bin_variable()

A binomial random variable is a discrete random variable that determines the number of times a specific event occurs in a given number of trials. Therefore, to construct a random variable we need to know the number of trials and the probability of success of the event we are interested in. To create it, we use the function bin_variable() as follows: 

```{r}
n <- 43 # the number of trials
p <- 0.4 # the probability of success per trial
X <- bin_variable(n,p) # calling our random variable X
```


##### Methods of bin.variable()

We can extract information about a random variable object by using methods like print.binvar(), summary.binvar() or print.summary.binvar() 

print.binvar() prints the content of our binomial object X. 

```{r}
print.binvar(X)
```

We use summary.binvar() to get a comprehensive summary of our binomial object X

```{r}
summary <- summary(X)
summary
```

print.summary.binvar() prints the summary of our binomial random variable
```{r}
print.summary.binvar(summary)
```

### 1. Measures of a binomial random variable

The mean of a binomial random variable is the expected number of successes in a given number of trials. We calculate the mean of our binomial object as follows:

```{r}
bin_mean(n,p)
```

We calculate the variance of our binomial object as follows:
```{r}
bin_variance(n,p)
```

The mode of a binomial random variable is the most likely number of success in a given number of independent trials rounded to the greatest integer less than or equal to it. We calculate the mode of our binomial object as follows:
```{r}
bin_mode(n,p)
```

The skewness of a probability distribution of a random variable measures the asymmetry of the probability distribution of a random variable about its mean. We calculate the skewness of the distribution of our binomial object as follows:
```{r}
bin_skewness(n,p)
```

The kurtosis of a probability distribution of a random variable measures the tailedness of the probability distribution of random variable. We calculate the kurtosis as follows
```{r}
bin_kurtosis(n,p)
```

### 3. Different Combinations of k Successes in n Trials

To calculate the different number of ways to obtain k successes in n trials we use bin_choose()
```{r}
k <- 37
bin_choose(n,k)
```
This means there are **6096454** ways of obtaining 37 successes in 43 trials. 






