---
title: "The Binomial Distribution of a Random Variable"
author: "Kaffa Sakho"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

## *Binomial Distribution* 

The package **"binomial"** is a set of functions that allow the computation and visualization of probabilities and other statistical measures of a **binomial random variable**.

The content of this guide for the binomial package is as follows: 

### 1. Creating a Binomial Random Variable Object: bin_var()

A binomial random variable is a discrete random variable that determines the number of times a specific event occurs in a given number of trials. Therefore, to construct a random variable we need to know the number of trials and the probability of success of the event we are interested in. We use the function bin_var() as follows: 

##### Methods of bin.var()

We can extract information about a random variable object by using print.binvar(), summary.binvar() or print.summary.binvar().

 **print.binvar()** prints 
2. Calculations on a random variable(mean,variance,mode,skewness,kurtosis)
3. find title for bin_choose()
4. Computing the Probabilities 
- explain what this means
- include the code 
5. Computing the distributi ons (both normal and cumulative)
- explain what they mean
- include the code
6. Visualizing Distributions of a Binomial Random Variable
- explain plot.bindis
- include graph
- explain plot.bincum
- include graph

## *Creating a Binomial Random Variable*

First, we need to create a random variable. define what a binomial ra
